eu-circle-torbay-precip.Rmd

### 2016-04-29 CORDEX/ensembles.Rmd

```{r, echo=FALSE}
for (i in 1:n) {
  ii <- is.element(toupper(IPCC.AR5.Table.9.A.1$Model.Name),toupper(gcmnm[i]))
  if (sum(ii)>0) {
    x <- c(as.character(IPCC.AR5.Table.9.A.1$Atmosphere.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Horizontal.Grid)[ii][1],
               IPCC.AR5.Table.9.A.1$Number.of.Vert.Levels[ii][1],
               IPCC.AR5.Table.9.A.1$Grid.Top.hPa[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Component.Name.or.type)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Atmos.Chemistry.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Land.Surface.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Ocean.Component.Name)[ii][1],
               IPCC.AR5.Table.9.A.1$Number.of.Vertical.Levels[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$z.Co.ord)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Ocean.Biogeochemistry.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Sea.Ice.Component.Name)[ii][1])
    print(x)
    X[i,] <- x
  }  else print(paste('no match for ',gcmnm[i]))
}
```

>>>>

```{r, echo=FALSE}
for (i in 1:n) {
  ii <- is.element(toupper(IPCC.AR5.Table.9.A.1$Model.Name),toupper(gcmnm[i]))
  if (sum(ii)>0) {
    x <- c(as.character(IPCC.AR5.Table.9.A.1$Atmosphere.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Horizontal.Grid)[ii][1],
               IPCC.AR5.Table.9.A.1$Number.of.Vert.Levels[ii][1],
               IPCC.AR5.Table.9.A.1$Grid.Top.hPa[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Component.Name.or.type)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Atmos.Chemistry.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Land.Surface.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Ocean.Component.Name)[ii][1],
               IPCC.AR5.Table.9.A.1$Number.of.Vertical.Levels[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$z.Co.ord)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Ocean.Biogeochemistry.Component.Name)[ii][1],
               as.character(IPCC.AR5.Table.9.A.1$Sea.Ice.Component.Name)[ii][1])
    #print(x)
    X[i,] <- x
  }  else print(paste('no match for ',gcmnm[i]))
}
```

### 2016-04-29 EU-Circle/eu-circle_case-study-3.Rmd

---------------------------------
```{r,eval=FALSE}
## Get MIDAS preciptation data that has laready been retrieved 
## from the MIDAS data base (UK Met Office)

@@

## Second weeding of stations with many missing values in annual 
## aggregate
nok <- apply(coredata(mu),2,'nv')
mu <- subset(mu,is=(nok>= 44))
fw<- subset(fw,is=(nok>= 44))

## Check the records
diagnose(mu)

##Fill in the remaining gaps using a PCA-based interpolation scheme 
pcafill(mu) -> mu
pcafill(fw) -> fw
```

@@

Most stations have the same features when it comes to a mean seasonal cycle in $\mu$, with the leading PCA accounting for 80\% of the variance.

@@

```{r}
if (!file.exists('dse.mu.eu-circle-worstcase.rda')) {
  dse.mu <- DSensemble.mu.worstcase(x,biascorrect=TRUE,mask=TRUE,
                                    lon=c(-80,20),lat=c(10,60),rel.cord=FALSE)
  save(file='dse.mu.eu-circle-worstcase.rda',dse.mu)
} else load('dse.mu.eu-circle-worstcase.rda')
plot(dse.mu[[1]])
```

>>>>

---------------------------------
```{r,eval=FALSE}
## Get MIDAS preciptation data that has laready been retrieved 
## from the MIDAS data base (UK Met Office)
load('pr.eu-circle-torbay.rda')
```

@@

## Second weeding of stations with many missing values in annual 
## aggregate
nok <- apply(coredata(mu),2,'nv')
mu <- subset(mu,is=(nok>= 44))
fw<- subset(fw,is=(nok>= 44))
```

Fill in missing values, but since there are too many missing values, we need to get some more data from the region. This is ok since we are working with annual aggregated values, which may imply larer spatial scales. In any case, these are used to assist the interpolation for the MIDAS sations.

```{r}
 ss <- select.station(param='precip',src='ecad',cntr=c('United Kingdom','France'),lat=c(45,55),lon=c(-10,0),nmin=50)
pr.ecad <- station(ss)
mu.ecad <- subset(annual(pr.ecad,'wetmean',nmin=100),it=c(1961,2011))
fw.ecad <- subset(annual(pr.ecad,'wetfreq',nmin=100),it=c(1961,2011))
## Second weeding of stations with many missing values in annual 
## aggregate
nok <- apply(coredata(mu.ecad),2,'nv')
mu.ecad <- subset(mu.ecad,is=(nok>= 50))
fw.ecad<- subset(fw.ecad,is=(nok>= 50))
diagnose(mu.ecad)
```

supplement these to the MIDAS data:

```{r}
mu <- combine.stations(mu,mu.ecad)
fw <- combine.stations(fw,fw.ecad)
```

```{r}
##Fill in the remaining gaps using a PCA-based interpolation scheme 
## Check the records
diagnose(mu)
pcafill(mu) -> mu
pcafill(fw) -> fw
```

@@

Most stations have the same features when it comes to a mean seasonal cycle in $\mu$, with the leading PCA accounting for 80% of the variance.

@@

Estimating upper-limits can be an additional approach to exploring the effect of temperature on the precipitation intensity. This is a cruder means for quantifying and may provide further information when more traditional methods give limited information.

```{r}
if (!file.exists('dse.mu.eu-circle-worstcase.rda')) {
  dse.mu <- DSensemble.mu.worstcase(x,biascorrect=TRUE,mask=TRUE,
                                    lon=c(-80,20),lat=c(10,60),rel.cord=FALSE,verbose=TRUE)
  save(file='dse.mu.eu-circle-worstcase.rda',dse.mu)
} else load('dse.mu.eu-circle-worstcase.rda')
plot(dse.mu[[1]])
```
